\TheTitle

### 2017-06-19 paper/lineval.tex
Format of the paper
Adding content for generalization and userstudy
This is just preliminary content for these sections, but it is heading
in the right direction.
Adding Tree size figure
Adds figure to paper, and to the makefile.
Preliminary future work section
Breaking User study section
Integrating the user study section of the paper into the rest of the
paper more cleanly.

The methodology section is nearly done, including information on user
selection, commit selection, and the questions for the study.

Updating the makefile to represent the changes.

\usepackage{tikz}
\usepackage{xcolor}
\usepackage{color}

@@

\newcommand{\TheTitle}{An evaluation and generalization of Merge-Tree}
\newcommand{\TheAuthors}{Evan Wilde, Daniel M. German}
\newcommand{\TheEmails}{etcwilde@uvic.ca, dmg@uvic.ca}
\newcommand{\TheSubject}{Testing the comprehension of users in large git repositories}
\newcommand{\TheKeywords}{Linux, git, data structures}

@@

>>>>

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{xcolor}
\usepackage{color}
\usepackage{listings}

@@

\newcommand{\TheTitle}{An Evaluation and Generalization of Merge-Tree}
\newcommand{\TheAuthors}{Evan Wilde, Daniel M. German}
\newcommand{\TheEmails}{etcwilde@uvic.ca, dmg@uvic.ca}
\newcommand{\TheSubject}{Testing the comprehension of users in large git repositories}
\newcommand{\TheKeywords}{Linux, git, visualizations}

\lstset{frame=tb,
  language=python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{chartblue},
  commentstyle=\color{chartred},
  stringstyle=\color{chartgreen},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

\section{Introduction}
\label{sec:introduction}

\input{introduction.tex}

\section{Related Works}
\label{sec:related_works}

\section{Methodology}
\label{sec:methodology}

\input{methodology.tex}

\section{Generalization}
\label{sec:generalization}

\input{generalization.tex}

\section{Results}
\label{sec:results}

\section{Discussion}
\label{sec:discussion}

\subsection{Future Work}
\label{sub:future_work}

\input{futurework.tex}

\section{Conclusion}
\label{sec:conclusion}

\nocite{*}

\bibliographystyle{IEEEtran}
\bibliography{references}
